Regional and Urban Economics

### 2023-02-20 Retail Agglomeration_Theory.qmd
kildr

The bid rent models are under the assumption that Dentists use spatial completion to maximise profit.
Nevertheless, the cost of dental care in Norway can vary depending on a number of other factors such as the type of treatment, the location of the dental practice and the dentist experience and qualifications.
The Norwegian Dental Association rate the average cost of check ups is between four to eight hundred Norwegian Krone's \@tannlege.
Bertrand model also take price as competitive advantage in to consideration.

@@

\
Shopping malls have a relatively short history in Norway, with the first shopping mall opening in the late sixties.
Prior to the most retail activities took place in the city centre.
Furthermore, these malls typically featured a mix of shops, restaurants and entertainment options, and they were often located in suburban areas or on the outskirts of cities \@home-n.
In resent years, there has been a trend towards larger and more comprehensive shopping malls in Norway \@home-n.

>>>>

The bid rent models are under the assumption that Dentists use spatial completion to maximise profit.
Nevertheless, the cost of dental care in Norway can vary depending on a number of other factors such as the type of treatment, the location of the dental practice and the dentist experience and qualifications.
The Norwegian Dental Association rate the average cost of check ups is between four to eight hundred Norwegian Krone's [@TannlegeforeningenTannlegeforeningen].
Bertrand model also take price as competitive advantage in to consideration.

@@

\
Shopping malls have a relatively short history in Norway, with the first shopping mall opening in the late sixties.
Prior to the most retail activities took place in the city centre.
Furthermore, these malls typically featured a mix of shops, restaurants and entertainment options, and they were often located in suburban areas or on the outskirts of cities [@NCSCNCSC2018].
In resent years, there has been a trend towards larger and more comprehensive shopping malls in Norway [@NCSCNCSC2018].
